Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2024-03-28 cis-perf-new-ll.tex
Updates from Overleaf

Denote the characteristics of episode $j$ as $\nu_j = (B_j, E_j, i(j))$.
I now define a series of sets $\set{E}_1, \dots, \set{E}_{N_E}, \set{E}_u$ and an integer $N_E$ such that any possible $\nu_j$ is in exactly one of the classes and each set corresponds to the possible infection episdoes that lead to identical observations (conditional on the test schedules).

@@

Otherwise, the sets are defined such that $\nu_j$ and $\nu_{j'}$ are in the same class if and only if $i(j) = i(j')$ and the episodes beginning and end times are censored to the same interval.
If $i \in \set{D}$ then there is exactly one $k$ such that $\set{E}_k$ is identical to $i$'s admissible region $\alpha_i$.
% In this case, I write $\alpha_{i(k)}$ to denote this admissible region.

More formally, the sets can be defined in terms of an equivalence relation $\equiv$ and two arbitrary possible episodes $j$ and $j'$.
Define $\nu_j \equiv \nu_{j'}$ to hold if and only if either both $j$ and $j'$ would be undetected (as defined in \cref{E-perf-test:sec:prob-undetected}) or the following four conditions all hold.
\begin{enumerate}
    \item Both $\nu_j$ and $\nu_{j'}$ would be detected.
    \item $i(j) = i(j')$.
    \item $\tau_{\sched_{i(j)}}(B_j) = \tau_{\sched_{i(j')}}(B_{j'})$, where $\tau$ is as defined in \cref{E-perf-test:eq:tau-def}.
    \item $\tau_{\sched_{i(j)}}(E_j) = \tau_{\sched_{i(j')}}(E_{j'})$.
\end{enumerate}
Then each $\set{E}_k$ is an equivalence class under this relation and the set of all possible $\nu_j$.
That is, taking any $k = 1, \dots, N_E, u$ then $\nu_j \in \set{E}_k$ and $\nu_{j'} \in \set{E}_k$ if and only if $\nu_j \equiv \nu_{j'}$.

Let $\xi_k$ denote $\prob(\nu_j \in \set{E}_k)$.
Assume, for tractability, that the events $\nu_j \in \set{E}_k$ and $\nu_{j'} \in \set{E}_{k'}$ are independent for $j \neq j'$.
Denote by $m_k$ then number of episodes in $\set{E}_k$.
$\vec{m} = [m_1, \dots m_{N_E}, m_u]^T$ are the observations.
Then:
\begin{align}
  \vec{m}
  \mid \ntot, \vec{\theta}
  \dist
  \MN\left(
    \ntot,
    \frac{1}{\Ncis}
    \begin{bmatrix}
        \xi_1 \\ \xi_2 \\ \vdots \\ \xi_{N_E} \\ \xi_u
    \end{bmatrix}
  \right).
  \label{perf-test:eq:alt-likelihood}
\end{align}

>>>>

Denote the characteristics of episode $j$ as $\nu_j = (B_j, E_j, i(j))$.
I now define an integer $N_E$ and a series of sets $\set{E}_1, \dots, \set{E}_{N_E}, \set{E}_u$ such that any possible $\nu_j$ is in exactly one of the classes and each set corresponds to the possible infection episodes that would generate identical observations (conditional on the test schedules).

@@

Otherwise, the sets are defined such that $\nu_j$ and $\nu_{j'}$ are in the same class if and only if $i(j) = i(j')$ and the episodes beginning and end times are censored to be in the same pair of intervals.
If $i \in \set{D}$ then there is exactly one $k$ such that $\set{E}_k$ is identical to $i$'s admissible region $\alpha_i$.
% In this case, I write $\alpha_{i(k)}$ to denote this admissible region.

More formally, the sets can be defined in terms of an equivalence relation $\equiv$ and two arbitrary possible episodes $j$ and $j'$.
Define $\nu_j \equiv \nu_{j'}$ to hold if and only if either both $j$ and $j'$ would be undetected (as defined in \cref{E-perf-test:sec:prob-undetected}) or the following four conditions all hold.
\begin{enumerate}
    \item Both $\nu_j$ and $\nu_{j'}$ would be detected.
    \item $i(j) = i(j')$.
    \item $\tau_{\sched_{i(j)}}(B_j) = \tau_{\sched_{i(j')}}(B_{j'})$, where $\tau$ is as defined in \cref{perf-test:eq:tau-def}.
    \item $\tau_{\sched_{i(j)}}(E_j) = \tau_{\sched_{i(j')}}(E_{j'})$.
\end{enumerate}
Then each $\set{E}_k$ is an equivalence class under this relation and the set of all possible $\nu_j$.
That is, taking any $k = 1, \dots, N_E, u$ then $\nu_j \in \set{E}_k$ and $\nu_{j'} \in \set{E}_k$ if and only if $\nu_j \equiv \nu_{j'}$.

Let $\xi_k$ denote $\prob(\nu_j \in \set{E}_k)$.
Assume, for tractability, that the events $\nu_j \in \set{E}_k$ and $\nu_{j'} \in \set{E}_{k'}$ are independent for $j \neq j'$.
Denote by $m_k$ the number of episodes in $\set{E}_k$.
$\vec{m} = [m_1, \dots m_{N_E}, m_u]^T$ are the observations.
Then:
\begin{align}
  \vec{m}
  \mid \ntot, \vec{\theta}
  \dist
  \MN\left(
    \ntot,
    \frac{1}{\Ncis}
    \begin{bmatrix}
        \xi_1 \\ \xi_2 \\ \vdots \\ \xi_{N_E} \\ \xi_u
    \end{bmatrix}
  \right).
  \label{perf-test:eq:alt-likelihood}
\end{align}

### 2024-03-28 cis-perfect-testing.tex
Updates from Overleaf

Any infection episode, whether detected or not, is fully characterised by the triplet $(b_j, e_j, i(j))$ where $b_j$ and $e_j$ are the times the episode begin and end respectively, and $i(j)$ is the individual the episode occurred in.
The episode's duration is $d_j = e_j - b_j + 1$ (see \cref{E-inc-prev:sec:definitions}).
For all $j$, the exact values $b_j$ and $e_j$ are latent.
If $j$ is undetected then $i(j)$ is also latent and nothing is known about $b_j$ or $e_j$.
If $j$ is detected, then $i(j)$ is known; $b_j \in [l_j^{(b)}, r_j^{(b)}]$; and $e_j \in [l_j^{(e)}, r_j^{(e)}]$.
These latter two properties are what make the data doubly interval censored.

@@

I will use these regions to form the data likelihood, conditional on $\ntot$.
The definition of the admissible region relies on the test results.
However the likelihood should be conditional only on $\vec{\theta}$, $\ntot$, and the test schedules.
Therefore, this is not strictly correct.
This issue can be rectified be considering the inadmissible region as many subregions each with an observed count of zero (sketched in \cref{perf-test:sec:alt-likelihood}).
Count zero regions do not contribute to the probability meaning the result is the same.
A formalisation of this approach requires much more complex notation for the same result; therefore, I prefer this presentation.

% Any episode $j$ independently belongs to one of these classes.
The probabilities $p_{iu}$, $p_{ia}$, and $p_{i\bar{a}}$ are conditional on the episode occurring in individual $i$.
I assume the individual in which an episode occurs is iid uniform across the cohort, that is $\prob(i(j) = i) = 1/\Ncis$.
Therefore, the conditional probabilities are multiplied by $1/\Ncis$ to form the unconditional probabilities.
For example, the probability of an episode being in class $\alpha_i$ is $p_{ia} / \Ncis$.

@@

Let $\na = (n_{1a}, \dots, n_{\Ncis a})^T$ be the vector of counts of episodes in the admissible classes.
This represents all the observations used in \cref{perf-test:eq:multinomial}.
Therefore, the posterior density we are interested in is $p(\vec{\theta} \mid \na)$.
It can be written as follows.
\begin{align}
p(\vec{\theta} \mid \na)
&\propto p(\vec{\theta}) p(\na \mid \vec{\theta}) \\
&= p(\vec{\theta}) \sum_{\ntot=\ndet}^\infty p(\ntot \mid \vec{\theta}) p(\na \mid \ntot, \vec{\theta})
\label{perf-test:eq:posterior1}
\end{align}
where the last line augments the likelihood with the total number of episodes, $\ntot$.

@@

I derive an analytical solution to $\eta$ (defined in \cref{perf-test:eq:eta}) under the prior $\ntot \dist \NBc(\mu, r)$.
I assume that $\vec{\theta}$, which are only the parameters of the survival distribution, has a prior independent of $\ntot$, the number of infections that occurred in the cohort.
Therefore, $p(\ntot \mid \vec{\theta}) = p(\ntot)$.

@@

% An episode is undetected if and only if no tests are performed during the episode or if there was no negative test prior to the episode.
% Equivalently, that the first test at or after $b$ is after $e$, or that there is no negative test prior to $b$.
To formalise this, first define $\tau_{\sched_i}(t)$ as the time until the next test at or after time $t$ in the schedule $\sched_i$:
\begin{align}
\tau_{\sched_i}(t) &= \min \{ t' \in \sched_i : t' \geq t \} - t
\label{perf-test:eq:tau-def}
\end{align}
defining $\min \emptyset = \infty$; \ie $\tau_{\sched_i}(t) = \infty$ if there is no $t' \in \sched_i$ such that $t' \geq t$.
The first condition can now be expressed as $e_j \geq b_j + \tau_{\sched_{i(j)}}(b_j)$.
Equivalently, $d_j \geq \tau_{\sched_{i(j)}}(b_j) + 1$.
The third condition can be expressed as $\tau_{\sched_{i(j)}}(b_j) < \infty$.

>>>>

Any infection episode, whether detected or not, is fully characterised by the triplet $(b_j, e_j, i(j))$ where $b_j$ and $e_j$ are the times the episode begin and end respectively; as $i(j)$ is the individual the episode occurred in it also identifies the test schedule.
The episode's duration is $d_j = e_j - b_j + 1$ (see \cref{E-inc-prev:sec:definitions}).
For all $j$, the exact values $b_j$ and $e_j$ are latent.
If $j$ is undetected then $i(j)$ is also latent and little is known about $b_j$ or $e_j$.
If $j$ is detected, then $i(j)$ is known; $b_j \in [l_j^{(b)}, r_j^{(b)}]$; and $e_j \in [l_j^{(e)}, r_j^{(e)}]$.
These latter two properties are what make the data doubly interval censored.

@@

I will use these regions to form the data likelihood, conditional on $\ntot$.
The definition of the admissible region relies on the test results.
However the likelihood should be conditional only on $\vec{\theta}$, $\ntot$, and the test schedules.
Therefore, this is not strictly correct.
This issue can be rectified be considering the inadmissible region as many subregions, which leads to the same result (sketched in \cref{perf-test:sec:alt-likelihood}).
A full formalisation of the derivation in \cref{perf-test:sec:alt-likelihood} would require much more complex notation for the same result; therefore, I prefer the presentation to follow.

% Any episode $j$ independently belongs to one of these classes.
The probabilities $p_{iu}$, $p_{ia}$, and $p_{i\bar{a}}$ are calculated conditional on the episode occurring in individual $i$.
I assume the individual in which an episode occurs is iid uniform across the cohort, that is $\prob(i(j) = i) = 1/\Ncis$.
Therefore, the conditional probabilities are multiplied by $1/\Ncis$ to form the probabilities .
For example, $\prob((B_j, E_j) \in \alpha_i, i(j) = i \mid \vec\theta) = p_{ia} / \Ncis$.

@@

Let $\na = (n_{1a}, \dots, n_{\Ncis a})^T$ be the vector of counts of episodes in the admissible classes.
This represents all the observations used in \cref{perf-test:eq:multinomial}.
Therefore, the posterior density we are interested in is $p(\vec{\theta} \mid \na)$.
It can be written as follows.
\begin{align}
p(\vec{\theta} \mid \na)
&\propto p(\vec{\theta}) p(\na \mid \vec{\theta}) \\
&= p(\vec\theta) \sum_{\ntot= \ndet}^{\infty} p(\ntot, \na \mid \vec{\theta}) \\
&= p(\vec{\theta}) \sum_{\ntot=\ndet}^\infty p(\ntot \mid \vec{\theta}) p(\na \mid \ntot, \vec{\theta})
\label{perf-test:eq:posterior1}
\end{align}
where the last line augments the likelihood with the total number of episodes, $\ntot$.

@@

I derive an analytical solution to $\eta$ (defined in \cref{perf-test:eq:eta}).
I assume the prior $\ntot \dist \NBc(\mu, r)$, independently of \vec{\theta}, the parameters of the survival distribution.
Therefore, $p(\ntot \mid \vec{\theta}) = p(\ntot)$.

@@

% An episode is undetected if and only if no tests are performed during the episode or if there was no negative test prior to the episode.
% Equivalently, that the first test at or after $b$ is after $e$, or that there is no negative test prior to $b$.
To formalise this, first define $\tau_{\sched_i}(t)$ as the time until the next test at or after time $t$ in the schedule $\sched_i$:
\begin{align}
\tau_{\sched_i}(t) &= \min \{ t' \in \sched_i : t' \geq t \} - t
\label{perf-test:eq:tau-def}
\end{align}
defining $\min \emptyset = \infty$; \ie $\tau_{\sched_i}(t) = \infty$ if there is no $t' \in \sched_i$ such that $t' \geq t$.
The first condition can now be expressed as $e_j \geq b_j + \tau_{\sched_{i(j)}}(b_j)$.
Equivalently, $d_j \geq \tau_{\sched_{i(j)}}(b_j) + 1$.
The fourth condition can be expressed as $\tau_{\sched_{i(j)}}(b_j) < \infty$.

### 2024-03-28 transmission.tex
Updates from Overleaf

In this chapter, I use the estimate of the distribution of the duration of RT-PCR positivity from combining information from the ATACCC and CIS studies (see \cref{E-imperf-test:sec:conclusion}) to investigate the feasibility of estimating incidence and transmission of SARS-CoV-2 from only the CIS data (described in \cref{E-intro:sec:cis}).
I will show that the CIS data are sufficient, demonstrating the value of surveys of this type for pandemic surveillance.

@@

I start with the backcalculation (\cref{backcalc}), based on \cref{E-inc-prev:eq:EPt}.
This approach enables estimation of incidence within (sub)populations of England.
There are several attractive features about this approach in the context here.
The backcalculation approach makes few assumptions about how transmission occurs; stronger assumptions increase the potential for introduce bias.
It can also easily incorporate arbitrary covariates to adjust for non-response bias.
The scale of the CIS and desire to correct for non-response bias presents challenges for this methodology, especially within the limited computation of the SRS environment.

In \cref{SEIR}, I use a mechanistic compartmental model, within the modelling framework introduced in \cref{E-SEIR:sec:mechanistic-models}.
This approach enables estimating both incidence and components of transmission.
Estimating transmission in addition to incidence answers important epidemiological questions, \eg whether changes in transmission can be explained by changes in contact rates.
I develop a novel observation model to allow the transmission model to be fit to the CIS data.

Finally, in \cref{transmission:sec:comparison}, I compare the results of the two approaches.
I show they give similar values, providing reassurance of the robustness of the results to modelling assumptions.
Overall, there is a bias-variance trade-off between the models.
Incidence and transmission have not previously been estimated from only SARS-CoV-2 prevalence surveys before.

@@

In this section, I apply the theory introduced in \cref{E-inc-prev} to estimate incidence.
I view the CIS as a series of daily, cross-sectional prevalence surveys.
This is the same approach as previously used to estimate prevalence from the CIS (see \cref{E-biology-data:sec:MRP}).

An important consideration in this section is non-response bias.
I correct for the non-response through the poststratification method introduced in \cref{E-biology-data:sec:MRP}.
Poststratification requires estimates of incidence in each stratum, before combining them to the target population and subpopulations of interest.
The strata are defined by at least age group, region, ethnicity, and sex due to differential non-response in the survey (see \cref{E-intro:sec:cis}).

@@

In \cref{E-inc-prev:sec:observation-process}, I showed that a deterministic approximation to the relationship between true prevalence and incidence is a good approximation for estimating incidence.
This relationship between incidence proportion and prevalence means that once one is inferred, the other is calculated via a deterministic function.
This gives two possible approaches for estimating incidence from prevalence data; in \cref{transmission:sec:backcalc-properties} I argue the second approach is more appropriate in this context.

@@

The first approach, which I call the \emph{incidence-inferred} approach, is a single statistical model where incidence is inferred, with prevalence as a derived quantity.
The basis of the statistical model, in a Bayesian framework, would be as follows.
\begin{align}
    \vec{Z} &\dist F_Z \\
    P_{i,t}  &= \sum_{k=0}^{d_\text{max}-1} Z_{i,t-k} S(k+1) \\
    \rho &\dist F_\rho \\
    Y_{i,t} \mid \vec{P}, \rho &\dist \BB(n_{i,t}, P_{i,t}, \rho)
\end{align}
where $\vec{Z}$ is a vector such that $Z_{i,t}$ is the incidence proportion in stratum $i$ on day $t$, with a joint prior $F_Z$; $P_{i,t}$ is the prevalence in stratum $i$ on day $t$; $\rho$ is the overdispersion parameter of the beta-binomial distribution (see \cref{E-distributions}) with prior $F_\rho$; $Y_{i,t}$ is the number of positive tests in stratum $i$ on day $t$; and $n_{i,t}$ is the number of tests in stratum $i$ on day $t$.
Fitting this model to a prevalence survey such as the CIS (\eg using MCMC) gives a posterior distribution of $\vec{Z}$, the target of inference.

The relationship between $\vec{P}$ and $\vec{Z}$ is from \cref{E-inc-prev:eq:EPt}, although dividing both sides by the stratum's population (assumed constant) to have the values in terms of incidence proportion and prevalence rather than incidence and number of prevalent individuals.

Specifying $F_Z$ would depend on the application of the approach, but should consider the need to provide structure to stabilise the problem (see \cref{E-intro:sec:disease-model}).
In the context of the CIS, it needs to allow borrowing information across time and/or strata (see \cref{E-biology-data:sec:MRP}).

@@

The incidence-inferred approach is more parsimonious in being a single step procedure.
However, computational considerations mean I favour the prevalence-inferred approach.

It will be convenient to define a variable equating to the quantity initially estimated.
Let $\pi_{i,t} = Z_{i,t}$ under the inference-inferred approach and $\pi_{i,t} = P_{i,t}$ is the prevalence.

The chosen approach should have the following properties.
\begin{enumerate}
    \item The prior should favour $\pi_{i,t}$ changing exponentially in $t$, \ie penalize changes from exponential growth.
        % Penalizing changes from continuous exponential growth is a natural formulation because mechanistic models predict exponential growth over short periods of time.
        Such penalization has previously been shown to improve estimates of SARS-CoV-2 prevalence by balancing over and under-fitting~\autocite{ealesAppropriately} and is the approach used for the CIS prevalence model (see \cref{E-biology-data:sec:MRP}).
    \item Limit estimates to epidemiologically and biologically plausible values.
        That is, incidence proportion and prevalence should be in the interval $[0, 1]$.
        % While incidence proportion can theoretically be greater than 1, this would imply that some individuals were infected multiple times in a day which is not biologically plausible.
    \item Have sufficient parameters to incorporate all necessary covariates to correct for non-response bias.
    \item Borrow information across the different covariates.
        The borrowing should penalize changes in the distribution of incidence/prevalence across strata in the same geographic region.
        A constant distribution is predicted by the theoretical study of epidemics, for example the dynamics of stratified, mechanistic transmission models (such as the one introduced in \cref{E-SEIR:sec:structured-populations}) when behavioural and immunity changes are negligible.
    \item Be computationally efficient.
        The model will be fit to granular data and therefore needs to be run within the SRS, with its computational limitations (see \cref{E-biology-data:sec:SRS}).
\end{enumerate}

>>>>

In this chapter, I use the estimate of the distribution of the duration of RT-PCR positivity from the combination of information from the ATACCC and CIS studies (see \cref{E-imperf-test:sec:conclusion}) to investigate the feasibility of estimating incidence and transmission of SARS-CoV-2 from only the CIS data (described in \cref{E-intro:sec:cis}).
I will show that the CIS data are sufficient, demonstrating the value of surveys of this type for pandemic surveillance.

@@

I start with the backcalculation (\cref{backcalc}), based on \cref{E-inc-prev:eq:EPt}, which enables estimation of incidence within (sub)populations of England.
The approach makes few assumptions about how transmission occurs, decreasing the potential to introduce bias and can also easily incorporate arbitrary covariates to adjust for non-response bias.
The scale of the CIS and desire to correct for non-response bias presents challenges for this methodology, especially within the limited computation of the SRS environment.

In \cref{SEIR}, I use a mechanistic compartmental model, within the modelling framework introduced in \cref{E-SEIR:sec:mechanistic-models}.
I estimate both incidence and several components of transmission.
Estimating transmission from CIS data requires developing a novel observation model.

Finally, in \cref{transmission:sec:comparison}, I compare the results of the two approaches.
I show they give similar values, providing reassurance of the robustness of the results to modelling assumptions.
% Overall, there is a bias-variance trade-off between the models.
% Incidence and transmission have not previously been estimated from only SARS-CoV-2 prevalence surveys before.

@@

In this section, I apply the theory introduced in \cref{E-inc-prev} to estimate incidence.
I view the CIS as a series of daily, cross-sectional prevalence surveys, as previously used to estimate prevalence (see \cref{E-biology-data:sec:MRP}).

An important consideration is non-response bias in the CIS study.
I correct for the non-response through the poststratification method introduced in \cref{E-biology-data:sec:MRP}.
Poststratification requires estimates of incidence in each stratum, before combining them to the target population and subpopulations of interest.
The strata are defined by at least age group, region, ethnicity, and sex due to differential non-response in the survey (see \cref{E-intro:sec:cis}).

@@

In \cref{E-inc-prev:sec:observation-process}, I showed that a deterministic approximation to the relationship between true prevalence and incidence is a good approximation for estimating incidence.
This means that once one of the two quantities is inferred, the other can be calculated via a deterministic function.
This gives two possible approaches for estimating incidence from prevalence data; in \cref{transmission:sec:backcalc-properties} I argue the second approach is more appropriate in this context.

@@

The first approach, which I call the \emph{incidence-inferred} approach, specifies a single statistical model including both incidence and prevalence.
The basis of this statistical model, in a Bayesian framework, would be as follows:
\begin{align}
    \vec{Z} &\dist F_Z \\
    P_{i,t}  &= \sum_{k=0}^{d_\text{max}-1} Z_{i,t-k} S(k+1) \\
    \rho &\dist F_\rho \\
    Y_{i,t} \mid \vec{P}, \rho &\dist \BB(n_{i,t}, P_{i,t}, \rho)
\end{align}
where $\vec{Z}$ is a vector such that $Z_{i,t}$ is the incidence proportion in stratum $i$ on day $t$, with a joint prior $F_Z$; $P_{i,t}$ is the prevalence in stratum $i$ on day $t$; $\rho$ is the overdispersion parameter of the beta-binomial distribution (see \cref{E-distributions}) with prior $F_\rho$; $Y_{i,t}$ is the number of positive tests in stratum $i$ on day $t$; and $n_{i,t}$ is the number of tests in stratum $i$ on day $t$.
Fitting this model to a prevalence survey such as the CIS gives a posterior distribution of $\vec{Z}$, the target of inference.
The relationship between $\vec{P}$ and $\vec{Z}$ is from \cref{E-inc-prev:eq:EPt}, although dividing both sides by the stratum's population (assumed constant) to have the values in terms of incidence proportion and prevalence rather than incidence and number of prevalent individuals.

Specifying $F_Z$ should consider the need to provide structure to stabilise the problem (see \cref{E-intro:sec:disease-model}).
In the context of the CIS, it needs to allow borrowing information across time and/or strata (see \cref{E-biology-data:sec:MRP}).

@@

The incidence-inferred approach is more parsimonious in being a single step procedure.
However, computational challenges make makes mean I favour the prevalence-inferred approach.

It will be convenient to define a variable equating to the quantity initially estimated.
Let $\pi_{i,t} = Z_{i,t}$ under the inference-inferred approach and $\pi_{i,t} = P_{i,t}$ under the prevalence-inferred approach.

The chosen approach should have the following properties.
\begin{enumerate}
    \item The prior for $\pi_{i,t}$ should favour $\pi_{i,t}$ changing exponentially in $t$, \ie penalize changes from exponential growth.
        % Penalizing changes from continuous exponential growth is a natural formulation because mechanistic models predict exponential growth over short periods of time.
        Such penalization has previously been shown to improve estimates of SARS-CoV-2 prevalence by balancing over and under-fitting~\autocite{ealesAppropriately} and is the approach used for the CIS prevalence model (see \cref{E-biology-data:sec:MRP}).
    \item Limit estimates to epidemiologically and biologically plausible values.
        That is, incidence proportion and prevalence should be in the interval $[0, 1]$.
        % While incidence proportion can theoretically be greater than 1, this would imply that some individuals were infected multiple times in a day which is not biologically plausible.
    \item Include sufficient parameters to incorporate all necessary covariates to correct for non-response bias.
    \item Borrow information across the different covariates.
        The borrowing should penalize changes in the distribution of incidence/prevalence across strata in the same geographic region.
        A constant distribution is predicted by the theoretical study of epidemics, for example the dynamics of stratified, mechanistic transmission models (such as the one introduced in \cref{E-SEIR:sec:structured-populations}) when behavioural and immunity changes are negligible.
    \item Be computationally efficient.
        The model will be fitted to granular data and therefore needs to be run within the SRS, with its computational limitations (see \cref{E-biology-data:sec:SRS}).
\end{enumerate}
